\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-20 body.tex
Save.
Save. Introduction.
Save. Add new section.
Save. Working on example section
Swap section meta-theory and impl. Please check Thm 3.1, justify that partial recursor is good enough.
Add Lang Design Section
Add appendix.

\section{Introduction}
\label{sec:intro}

@@

>>>>

\section{Introduction}
\label{sec:intro}
\input{introduction.tex}

% Concept 
% Contribution

\section{Language Design}
% what feature we want
% what problem/formalization we want to achieve
% Before/After Comparison of examples (with/without Fampoly)
\label{sec:lang-design}
\input{lang-design.tex}

% Macro for all use

\newcommand{\denotes}[1]{{\llbracket {#1} \rrbracket}}
\newcommand{\denotesS}[1]{{{\llbracket {#1} \rrbracket}_S}}
\newcommand{\goodCtx}[2]{{ {#1} \ \vdash }}
\newcommand{\goodType}[3]{{ {#1} \vdash {#2} }}
\newcommand{\goodTerm}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSub}[3]{{ {#1} \vdash {#2} : {#3} }}
\newcommand{\goodSig}[3]{{ {#1} \vdash {#2} \ \  Sig^{#3} }}
\newcommand{\goodWSig}[3]{{ {#1} \vdash {#2} \ \ WSig^{#3} }}
\newcommand{\goodSeal}[4]{{ {#1} \vdash {#2} : {#3} \  |\  {#4} }}
\newcommand{\goodInh}[4]{{ {#1} \vdash {#2} : {#3} \twoheadrightarrow {#4}}}
\newcommand{\nat}{\mathbf{N}}

\newcommand{\cU}{{\mathcal{U}}}
\newcommand{\cB}{{\mathbb{B}}}
\newcommand{\cL}{{\mathcal{L}}}
\newcommand{\cC}{{\mathcal{C}}}
\newcommand{\cCt}{{\mathcal{C}_t}}
\newcommand{\bW}{{\mathbb{W}}}

\section{Prototypical Coq Implementation}
% we need to make this section before Metatheory
% because a lot of our formulation in the metatheory
%   is inspired by the implementation
\label{sec:coqimpl}
\input{coqimpl.tex}

\section{Metatheory}

\label{sec:metatheory}
\input{metatheory.tex}

\section{Example}\label{sec:coqexample}
\input{coq-example.tex}

@@

\appendix

\section{Metatheory in (pseudo-)Agda}
We make three agda source code files (publicly and anonymously) openly avaliable that include the corresponding QIIT syntax definition and models.

For syntax, please check \href{https://drive.google.com/file/d/1aoG67rmXzP_x1MvZCIN3do0sucyqjwkn/view?usp=sharing}{here}.

For consistency model, please check \href{https://drive.google.com/file/d/1pNhnn125P5byAHDaSIlpbxMvr1F-9FRo/view?usp=sharing}{here}.

For canonicity model, please check \href{https://drive.google.com/file/d/1R6C7QNfyu8fbl6LE2ruvpqZ_ZDSRVo0c/view?usp=sharing}{here}.

We suggest using editors with proper syntax highlighting, e.g. VSCode with agda-code plugins.

### 2022-06-20 coq-example.tex
Add appendix.

Our emphasis here is that, we singled out some programming language features from STLC and prove the type safety for each feature separately, following the style of the examples in MTC~\cite{delaware2013,forsta2020}. And we use a \textit{not-yet-formally-defined} \textbf{mix-in} feature to mix the semantic and properties of two programming language feature---product and boolean---with vanilla STLC. This way, we can say precisely, \textit{a programming language feature itself is a piece of data/inheritance judgement/inherited family}. Compared to MTC, our example uses small-step operational semantic by exploiting the extensible inductive type, and most of the proof is directly adapted from the one in Software Foundation, resulting a more accessible proof. 
% In related work, Coq/Metatheory a la carte/Tion embedding can be emphasized as a more "semantic approach" because they encode the meaning using a special design pattern (for example, open recursive inductive type for extension), compared to our more syntactic approach. Their advantage is the transferability of this technique accross different proof assistants, and their disadvantage is that their approach are less accessible and unfriendly to amateur Coq users---which can be reflected from the distance of their approach and text-book Software Foundation proof.

>>>>

Our emphasis here is that, we singled out some programming language features from STLC and prove the type safety for each feature separately, following the style of the examples in MTC~\cite{delaware2013,forsta2020}. And we use a \textit{not-yet-formally-defined} \textbf{mix-in} feature to mix the semantic and properties of two programming language feature---product and boolean (in \cref{fig:STLC-example})---with vanilla STLC. This way, we can say precisely, \textit{a programming language feature itself is a piece of data/inheritance judgement/inherited family}. Compared to MTC, our example uses small-step operational semantic by exploiting the extensible inductive type, and most of the proof is directly adapted from the one in Software Foundation, resulting a more accessible proof. 
% In related work, Coq/Metatheory a la carte/Tion embedding can be emphasized as a more "semantic approach" because they encode the meaning using a special design pattern (for example, open recursive inductive type for extension), compared to our more syntactic approach. Their advantage is the transferability of this technique accross different proof assistants, and their disadvantage is that their approach are less accessible and unfriendly to amateur Coq users---which can be reflected from the distance of their approach and text-book Software Foundation proof.
